---
title: "Influencer Marketing Study 2"
output: 
  github_document:
    toc: true
date: "2025-03-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Upload data, select rows and columns
```{r}
data <- read_csv("../Data/im_study2_results.csv")

data <- data[3:318,]

clean_data <- data %>% select(-StartDate, -EndDate, -Status, -Progress, -Finished, -RecordedDate, -RecipientFirstName, -RecipientLastName, -RecipientEmail, -ExternalReference, -DistributionChannel, -UserLanguage, -LocationLatitude, -LocationLongitude)
```

Remove respondents that are not female, finished too quickly or failed attention checks for brand & product
```{r}
clean_data <- clean_data %>% filter(Q22=="Female")

hist(as.numeric(clean_data$`Duration (in seconds)`)/60, main="Duration in Minutes")
min(as.numeric(clean_data$`Duration (in seconds)`)/60)
mean(as.numeric(clean_data$`Duration (in seconds)`)/60)
median(as.numeric(clean_data$`Duration (in seconds)`)/60)

#pass attention check
clean_data <- clean_data %>% filter(Q14=="Cup")

#who posted the ad?
clean_data %>% group_by(Q42) %>% dplyr::summarise(n=n())

#who was the influencer?
clean_data %>% group_by(Q16) %>% dplyr::summarise(n=n())

#who was the brand?
clean_data %>% group_by(Q58) %>% dplyr::summarise(n=n())
```

# Social Media Usage 

```{r}
clean_data %>%
  ggplot(aes(x=Q1, y=after_stat(prop), group=1)) + 
  geom_bar() + 
  scale_y_continuous(labels = scales::percent_format()) +  # Convert to percentage format
  labs(y="", x="", title="Do you use any form of social media?") + theme_minimal()

#other includes reddit, youtube, twitter, tumblr, blue sky, discord, snapchat, and a couple others 
#unique(clean_data$Q5_6_TEXT)

# Separate multiple selections into individual rows
social_media_counts <- clean_data %>%
  separate_rows(Q5, sep = ",") %>%  # Split at commas into separate rows
  count(Q5) %>%  # Count occurrences of each platform
  mutate(percent = (n /nrow(clean_data)) * 100)  # Calculate percentage

social_media_colors <- c(
  "Facebook" = "#1877F2",    # Facebook Blue
  "Instagram" = "#E4405F",   # Instagram Pink/Red
  "TikTok" = "#000000",      # TikTok Black
  "Pinterest" = "#E60023",   # Pinterest Red
  "Linkedin" = "#0077B5",    # LinkedIn Blue
  "Twitter" = "#1DA1F2",     # Twitter Blue
  "Snapchat" = "#FFFC00",    # Snapchat Yellow
  "YouTube" = "#FF0000"      # YouTube Red
)

social_media_counts %>% arrange(percent) %>% 
  ggplot(aes(x=Q5, y=percent, fill=Q5)) + 
  geom_col(show.legend = FALSE) +  # Use geom_col() since we precomputed counts
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format percentages
  labs(y="Percentage of Respondents", x="", 
       title="Social Media Usage Distribution") + 
  theme_minimal() +  # Use geom_col() for precomputed counts
  scale_fill_manual(values = social_media_colors) + theme(axis.text.x = element_text(angle = 45, hjust = 1))

clean_data %>%
  ggplot(aes(x=Q6, y=after_stat(prop), group=1)) + 
  geom_bar() + 
  scale_y_continuous(labels = scales::percent_format()) +  # Convert to percentage format
  labs(y="", x="", title="How many hours per day do you spend on social media?") + theme_minimal()

clean_data %>%
  ggplot(aes(x=Q20, y=after_stat(prop), group=1, fill=Q20)) + 
  geom_bar() + 
  scale_y_continuous(labels = scales::percent_format()) +  # Convert to percentage format
  labs(y="", x="", title="What is your main purpose for using social media?") + theme_minimal() + coord_flip()
```
Influencer Content

56% of people say they interact with influencer content daily, and 29% say 2-3 times per week. 
```{r}
#how often do you interact with influencer content
clean_data %>% group_by(Q21) %>% summarise(n=n()/nrow(clean_data))

#which influencers do you know
clean_data %>% group_by(Q40) %>% summarise(n=n())

# Convert to tidy format
response_df <- clean_data %>%
  separate_rows(Q40, sep = ",") %>%
  mutate(Q40_response = str_trim(Q40))  # remove leading/trailing spaces

# Count and plot
response_df %>%
  count(Q40_response, sort = TRUE) %>%
  ggplot(aes(x = fct_reorder(Q40_response, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Influencers Recognized by Respondents",
    x = "",
    y = "Number of Respondents"
  ) +
  theme_minimal(base_size = 14)
```

# Influencer vs Brand 

Only 51% of those assigned to the brand group correctly identified that it was the brand who posted the advertisement. 98% of those assigned to the influencer group correctly identified that an influencer posted the ad (the rest chose celebrity). Of those who selected an influencer posted the brand (from either treatment group) 68% correctly chose Sienna Blake as the influencer, and about 27% said they don't know or remember. Of those who said the brand posted, 100% correctly identified the brand as Siply. 
```{r}
clean_data %>% group_by(adType) %>% summarise(n=n()/nrow(clean_data))

brand_data <- clean_data %>% filter(adType=="Brand")
brand_data %>% group_by(Q42) %>% summarise(n=n()/nrow(brand_data))

influencer_data <- clean_data %>% filter(adType=="Influencer")
influencer_data %>% group_by(Q42) %>% summarise(n=n()/nrow(influencer_data))

clean_data %>%
  filter(!is.na(Q16)) %>%
  group_by(Q16) %>%
  summarise(n = n()) %>%
  mutate(percent = scales::percent(n / sum(n)))

clean_data %>%
  filter(!is.na(Q58)) %>%
  group_by(Q58) %>%
  summarise(n = n()) %>%
  mutate(percent = scales::percent(n / sum(n)))
```

# Purchase Likelihood 

Q69_1: Across all respondents about 30% said they were unlikely to purchase the siply cup, 26% said likely and 22% said very unlikely. There is a not a statistically significant difference in purchase likelihood between the influencer and the brand group. "prop 1" is brand and "prop 2" is influencer. What about those who thought it was influencer vs those who thought it was a brand? There is still not a statistically significant difference in purchase likelihood between those who thought it was a brand or those who thought it was an influencer ("prop 2" is influencer is a little higher). 
```{r}
clean_data %>% group_by(Q69_1) %>% summarise(n=n()/nrow(clean_data))

clean_data <- clean_data %>%
  mutate(purchase_binary = ifelse(Q69_1 %in% c("Likely", "Very likely"), 1, 0))

summary_df <- clean_data %>%
  filter(!is.na(purchase_binary), !is.na(adType)) %>%
  group_by(adType) %>%
  summarise(n = n(), n_yes = sum(purchase_binary), prop = mean(purchase_binary))

# Proportion test
prop.test(x = summary_df$n_yes, n = summary_df$n)

#based on their response instead of actual 
summary_df2 <- clean_data %>%
  filter(!is.na(purchase_binary), Q42 %in% c("Brand", "Influencer")) %>%
  group_by(Q42) %>%
  summarise(n = n(), n_yes = sum(purchase_binary), prop = mean(purchase_binary))

# Proportion test
prop.test(x = summary_df2$n_yes, n = summary_df2$n)
```
# Mood

Numeric T test: Those who saw the influencer ad were statistically significant (at 90% level) higher mean values of Determined, Excited, Inspired, Alert, Active, Strong, Proud, Scared, Afraid, Upset, Guilty, and Hostile. Those who saw the influencer ad were statistically significant (at 95% level) higher mean values of Determined, Excited, Inspired, Alert, Active, Strong, Proud, Scared, Guilty, and Hostile.
```{r}
likert_to_num <- function(x) {
  recode(x,
    "Very slightly or not at all" = 1,
    "A little" = 2,
    "Moderately" = 3,
    "Quite a bit" = 4,
    "Extremely" = 5,
    .default = NA_real_
  )
}

mood_items <- c("Q37_1", "Q37_2", "Q37_3", "Q37_4", "Q37_5", "Q37_6", "Q37_7", "Q76_1", "Q76_2", "Q76_3", "Q76_4", "Q76_5", "Q76_6", "Q76_7", "Q80_1", "Q80_2", "Q80_3", "Q80_4", "Q80_5", "Q80_6" )

clean_data[mood_items] <- lapply(clean_data[mood_items], likert_to_num)

results <- lapply(mood_items, function(item) {
  t.test(as.formula(paste(item, "~ adType")), data = clean_data)
})

results_summary <- data.frame(
  item = mood_items,
  p_value = sapply(results, \(x) x$p.value),
  mean_brand = sapply(results, \(x) x$estimate[1]),
  mean_influencer = sapply(results, \(x) x$estimate[2])
)

sig10_moods <- c("Determined", "Excited", "Inspired", "Alert", "Active", "Strong", "Proud", "Scared", "Afraid", "Upset", "Guilty", "Hostile")
results_summary %>% filter(p_value < .10) %>% bind_cols(sig10_moods)

sig5_moods <- c("Determined", "Excited", "Inspired", "Alert", "Active", "Strong", "Proud", "Scared", "Guilty", "Hostile")
results_summary %>% filter(p_value < .05) %>% bind_cols(sig5_moods)
```
Non-parametric Wilcoxon Test: Those in the influencer group are statistically significantly (5% level) higher in moods Determined, Excited, Inspired, Alert, Active, Strong, Proud, and Hostile. (does not have scared and guilty like t test did) 
```{r}
results2 <- lapply(mood_items, function(item) {
  wilcox.test(as.formula(paste(item, "~ adType")), data = clean_data)
})

results_summary2 <- data.frame(
  item = mood_items,
  p_value = sapply(results2, \(x) x$p.value),
  mean_brand = sapply(mood_items, function(item) {
    mean(clean_data[[item]][clean_data$adType == "Brand"], na.rm = TRUE)
  }),
  mean_influencer = sapply(mood_items, function(item) {
    mean(clean_data[[item]][clean_data$adType == "Influencer"], na.rm = TRUE)
  })
)

wilcox_sig_moods <- c("Determined", "Excited", "Inspired", "Alert", "Active", "Strong", "Proud", "Hostile")

results_summary2 %>% filter(p_value<0.05) %>% bind_cols(wilcox_sig_moods)
```

# Social State Self Esteem 

Only the "I feel self concious" is higher for those who were in the influencer group at the 10% significance level. No differences at the 5% significance level. 
```{r}
likert_to_num <- function(x) {
  recode(x,
    "1 (Not at all)" = 1,
    "2 (A little bit)" = 2,
    "3 (Somewhat)" = 3,
    "4 (Very much)" = 4,
    "5 (Extremely)" = 5,
    .default = NA_real_
  )
}

social_items <- c("Q17_1", "Q17_2", "Q17_3", "Q17_4", "Q17_5", "Q17_6", "Q17_7")

clean_data[social_items] <- lapply(clean_data[social_items], likert_to_num)

results3 <- lapply(social_items, function(item) {
  t.test(as.formula(paste(item, "~ adType")), data = clean_data)
})

results_summary3 <- data.frame(
  item = social_items,
  p_value = sapply(results3, \(x) x$p.value),
  mean_brand = sapply(results3, \(x) x$estimate[1]),
  mean_influencer = sapply(results3, \(x) x$estimate[2])
)

#no significant difference at the 5% level in social state self esteem
results_summary3 %>% filter(p_value < .05)

# I feel self conscious is higher for those who saw the influencer ad at the 10% significance level 
results_summary3 %>% filter(p_value < .10)
```

# Appearance State Self Esteem 

At the 95% significance level, those who saw the influencer ad rated higher on "I feel good about myself" and "I am pleased with my appearance right now". Those who saw the brand ad rated higher on "I feel unattractive".
```{r}
appearance_items <- c("Q59_1", "Q59_2", "Q59_3", "Q59_4", "Q59_5", "Q59_6")

clean_data[appearance_items] <- lapply(clean_data[appearance_items], likert_to_num)

results4 <- lapply(appearance_items, function(item) {
  t.test(as.formula(paste(item, "~ adType")), data = clean_data)
})

results_summary4 <- data.frame(
  item = appearance_items,
  p_value = sapply(results4, \(x) x$p.value),
  mean_brand = sapply(results4, \(x) x$estimate[1]),
  mean_influencer = sapply(results4, \(x) x$estimate[2])
)

#At the 95% significance level, those who saw the influencer ad rated higher on "I feel good about myself" and "I am pleased with my appearance right now". Those who saw the brand ad rated higher on "I feel unattractive". 
results_summary4 %>% filter(p_value < .05)
```

# Stimuli 

88% said they have never heard of the brand used in the study "Siply". 92% said they have never heard of the influencer used in the study "Sienna Blake". 42% of respondents thought Siply was AI generated, 61% said Sienna Blake was AI generated.  
```{r}
#have you heard of the brand Siply
clean_data %>% group_by(Q88) %>% summarise(n=n()/nrow(clean_data))

#have you heard of the influencer Sienna Blake
clean_data %>% group_by(Q89) %>% summarise(n=n()/nrow(clean_data))

#is siply real
clean_data %>% group_by(Q92_1) %>% summarise(n=n()/nrow(clean_data))

#is Sienna Blake real
clean_data %>% group_by(Q92_2) %>% summarise(n=n()/nrow(clean_data))
```


# Demographics 

63% of respondents are 25-34 years old, 30% are 18-24 years old and 6% are 35-44 years old (which should just be 35 based on my Prolific screeners). 47% work full time, 44% have never been married and 33% are married. Most people have income between %25k-$100k. 
```{r}
#age
clean_data %>% group_by(Q7) %>% summarise(n=n()/nrow(clean_data))

#employment status
clean_data %>% group_by(Q9) %>% summarise(n=n()/nrow(clean_data))

#marital status
clean_data %>% group_by(Q10) %>% summarise(n=n()/nrow(clean_data))

#income
clean_data %>% group_by(Q47) %>% summarise(n=n()/nrow(clean_data))
```



